---
title: "Assignment Template"
author: "Dr Thomas Robinson and Dr Dan de Kadt"
date: "AT 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # Note: different from .Rmd default
```

This document contains the necessary commands and layout to meet the formatting requirements for MY472. You should use the template.Rmd file as the basis for your own answers to the assigned exercises.

## Formatting requirements

* You must present all results in full sentences, as you would in a report or academic piece of writing
  
  * If the exercise requires generating a table or figure, you should include at least one sentence introducing and explaining it. E.g. "The table below reports the counts of Wikipedia articles mentioning the LSE, by type of article."

* Unless stated otherwise, all code used to answer the exercises should be included at the end of the script

* Code should be annotated with comments, to help the marker understand what you have done

* Your output should be replicable. Any result/table/figure that cannot be traced back to your code will not be marked

## Example of in-line figures without code

For those interested, we achieve the formatting requirements in two-steps: 1) in the `setup` chunk, we set `knitr::opts_chunk$set(echo = FALSE)` so that code is not included (echoed) by default in code chunks; 2) we add a specific chunk at the end of the file to collect and print *all* the code in the Rmarkdown file. Do not delete the final code chunk from the template!

For example, below we use a code chunk to generate random data and include a scatter plot in-line. The code used to generate this chart is only reported at the end of the document. 

```{r plot_example}
set.seed(89)
x <- rnorm(100)
y <- rnorm(100)
plot(x,y)
```

In specific instances, however, you may be directed to report your code in-line (or you may want to do this to illustrate a specific point). In these cases, we can override the default behaviour by adding the chunk option `echo = TRUE` to a specific R chunk. When `echo=TRUE`, your code is presented in-line with any output displayed afterwards. The same code will also be included in the appendix at the bottom of the document (which is fine).

```{r echo_example, echo=TRUE}
# Make sure to annotate your code effectively
print("This command is visible in-line.")
```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
